Distributed Nonlinear Control Design using Separable Control Contraction Metrics

### 2017-06-05 R0V0.tex
Change Corollary 1: formulation considering also the input variable u and the sign of the identity

\begin{corollary}[{\cite{SteinShiromotoManchester2016}}]\label{cor:main result}
	Assume that the matrix $A$ depends only on the system state $x$, the matrix $B$ satisfies the identity
	\begin{equation*}
		\partial_BW-\tfrac{\partial B}{\partial x}W+W\tfrac{\partial B}{\partial x}^\top\equiv0
	\end{equation*}
	and there exist $N$ functions $\rho_i:\mathbb{R}^{n_i+\vec{n}_i}\to\mathbb{R}$ such that the matrix inequality
	\begin{equation}\label{eq:with R}
		-\dot{W}+\tfrac{\partial f}{\partial x}W+W\tfrac{\partial f}{\partial x}^\top-BRB^\top-2\lambda W\prec0
	\end{equation}
	holds uniformly with respect to $x\in\mathbb{R}^n$, where $R=\mathbin{\mathtt{diag}}(\rho_1,\ldots,\rho_N)$. Then, $W$ is a sum-separable control contraction metric for system~\eqref{eq:general system} and there exists a solution to Problem~\ref{problem formulation}. In particular, the graph $\mathscr{G}_c$ describing the communication network among different controllers specifies the functions $\rho_i$.
\end{corollary}

>>>>

\begin{corollary}[{\cite{SteinShiromotoManchester2016}}]\label{cor:main result}
	Assume that the matrix $B$ satisfies the identity
	\begin{equation*}
		\partial_BW-\tfrac{\partial B}{\partial x}W-W\tfrac{\partial B}{\partial x}^\top\equiv0
	\end{equation*}
	and there exist $N$ functions $\rho_i:\mathbb{R}^{n_i+\vec{n}_i}\to\mathbb{R}$ such that the matrix inequality
	\begin{equation}\label{eq:with R}
		-\dot{W}+\tfrac{\partial f}{\partial x}W+W\tfrac{\partial f}{\partial x}^\top-BRB^\top-2\lambda W\prec0
	\end{equation}
	holds uniformly with respect to $(x,u)\in\mathbb{R}^n\times\mathbb{R}^m$, where $R=\mathbin{\mathtt{diag}}(\rho_1,\ldots,\rho_N)$. Then, $W$ is a sum-separable control contraction metric for system~\eqref{eq:general system} and there exists a solution to Problem~\ref{problem formulation}. In particular, the graph $\mathscr{G}_c$ describing the communication network among different controllers specifies the functions $\rho_i$.
\end{corollary}
